Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
pass on 5.0

This section describes the infrastructure we used for cross-engine
differential testing. Figure~\ref{fig:workflow} illustrates the
workflow of the approach. It takes on input a list of JS files and
generates warnings on output. Numbered boxes in the figure denote the
data processors and arrowed lines denote data flows. The cycle icons
indicate repetition--the leftmost icon indicates that each file in the
input list will be analyzed in separate whereas the rightmost icon
shows that a single file will be fuzzed multiple times.

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 0 0 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

The bug-finding process works as follows. For a given test input, the
toolchain produces new inputs using some off-the-shelf input fuzzer
(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
selected.)  Then, the oracle checks whether or not the output produced
for the fuzzed file is consistent across all engines (step 2). In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure ignores the
input. Otherwise, it considers the input as potentially
fault-revealing; hence, interesting for human inspection. Finally, to
facilitate the human inspection process, the infrastructure
prioritizes warnings and clusters them in groups (step 3). We describe
these features in Sections~\ref{sec:prioritization} and
\ref{sec:clusterization}. Note that a number of reasons exist, other
than a bug, for discrepancy to arise (see
Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}) and there is no clear automatic approach
to precisely distinguish false and true positives. As such, a human
needs to inspect the warning to classify the issue. As mentioned
earlier, this justifies why differential testing is challenging to
automate at the functional level. Existing techniques that use
differential testing control rate of false alarms differently. For
example, Mozilla uses varies the configurations of thei
\smonkey\ engine, but the implementation is the
same~\cite{mozilla-severity}. The sources of non-determinism are
therefore similar. CSmith~\cite{Yang:2011:FUB:1993498.1993532}
addresses the problem by trying to avoid generating C files that
produce undefined behavior. However, mapping all sources of
undefinedness in JS is impractical.

For step 2, we considered using the open-source tool
eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
output discrepancy. However, we noticed that eshost-cli does not
handle discrepancies involving crashes, \Igor{If the criteria is to
find crashes or fatal errors, it is possible to run the
infrastructure with any runner(?) tool, including the
javascript binaries itself.}. As such, we forked the
eshost-cli GitHub project and implemented that functionality on it. It
is also important to note that our checker does not support the case
where the test fails in all engines but the kind of failure (\eg{},
exception thrown) is different. Currently, our infrastructure does not
report discrepancy for that case. For that, it would be necessary to
properly parse the error message to retrieve the error types. We left
that as future work as we already found several discrepancies even
without that.

>>>>

This section describes the infrastructure we used for cross-engine
differential testing. Figure~\ref{fig:workflow} illustrates the
workflow of the approach. It takes on input a list of JS files and
generates warnings on output. Numbered boxes in the figure denote the
data processors and arrowed lines denote data flows. The cycle icons
indicate repetition--the cycle icon close to the cylinder icon
indicates that each file in the input list will be analyzed in
separate whereas the other cycle icon shows that a single file will be
fuzzed multiple times.

\begin{figure}[t]
  \centering
  \includegraphics[trim=0 0 0 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure
    overview.\Fix{tem certeza que Hermes estah usando mesma fonte/tamanho?}}
\end{figure}

The bug-finding process works as follows. First, for a given test
input, the toolchain produces new inputs using some off-the-shelf
input fuzzer (step 1). Section~\ref{sec:objects:fuzzers} describes the
fuzzers we selected. Then, the oracle checks whether or not the output
produced for the fuzzed file is consistent across all engines (step
2). In case the test passes in all engines or fails in all engines
(\ie{}, the output is consistent), the infrastructure ignores the
input. Otherwise, it considers the input as potentially
fault-revealing; hence, interesting for human inspection. Finally, to
facilitate the human inspection process, the infrastructure
prioritizes warnings and clusters them in groups (step 3). We describe
these features in Sections~\ref{sec:prioritization} and
\ref{sec:clusterization}. Note that a number of reasons exist, other
than a bug, for discrepancy to arise (see
Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}) and there is no clear automatic approach
to precisely distinguish false and true positives. As such, a human
needs to inspect a warning to classify the issue. As mentioned
earlier, this justifies why differential testing is challenging to
automate at the functional level. Existing techniques that use
differential testing deal with false alarms differently. For example,
Mozilla varies the configurations of their \smonkey\ engine, but the
implementation is the same~\cite{mozilla-severity}. Non-determinism is
therefore more likely to be associated with the variations across
version as these version use the same core
implementation. CSmith~\cite{Yang:2011:FUB:1993498.1993532} addresses
the problem by trying to avoid generating C files that produce
undefined behavior. Mapping all sources of undefinedness in JS is
impractical.

%\Igor{If the criteria is to find crashes or fatal errors, it is
%possible to run the infrastructure with any runner(?) tool, including
%the javascript binaries itself.}

For step 2, we considered using the open-source tool
eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
output discrepancy. However, we noticed that eshost-cli does not
handle discrepancies involving crashes. As such, we forked the
eshost-cli GitHub project and implemented that functionality on it. It
is important to note that our checker does not support the case where
the test fails in all engines with a different kind of failure as it
is unclear how to properly relate those failures. Currently, our
infrastructure does not report discrepancy on that case. We left that
as future work as we already found several discrepancies even without
that.

%% For that, it would be
%% necessary to properly parse the error message to retrieve the error
%% types.
